---
title: "DAO Creators Survey"
author: "Gitcoin x Bankless"
date: "8/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

Load libraries and data. Shorten column names to make it manageable.

```{r, echo=FALSE}
# load libraries
library(tidyverse)
library(tidytext)

# load data
df <- read_csv("./DAO_Worker_Report_Sep1.csv")

# Rename
df1 <- df %>%
    # Rename: shorten column names to be manageable
    rename(
       timestamp = "Timestamp",
       daos_work_for = "what DAO(s) do you work for? for each DAO, how many hours/month do you work? (feel free to include multiple)",
       city = "what city are you based in?",
       twitter = "whats your twitter username?",
       eth_addr = "whats your ETH address?",
       task = "what kind of work do you do? (eg ops, coder, design, etc)",
       task_assign = "how are tasks assigned? how does your DAO decide what you’re doing and how much to pay you?",
       day_to_day = "what is your day to day like?",
       resume = "do you have a DAO version of “resume”? what does it look like?",
       improve_coord = "are there any opportunities to improve the way your work is coordinated?  if so what are they?",
       web3_tool = "what web3 tools are used to coordinate/allocate resources?",
       usd_earning = "how much do you make in USD equivilent per month?",
       income_stability = "is your income stability a priority for you?  does your DAO meet your expectations on income stability?",
       primary_income = "are DAOs your primary source of income?",
       token_volatility = "how do you handle token volatility?",
       health_insurance = "where do you get health insurance?",
       retirement = "are you saving for retirement?",
       tax = "how do you do compliance with local taxation/legal requirements for workers?",
       dispute = "what do you do if there is a dispute between yourself and the DAO? or another DAO member?",
       visa = "how do you manage visas to travel/work abroad?",
       dao_different = "what is the most different/interesting thing about working for a DAO to you?",
       favorite = "what is your favorite part of working for a DAO?",
       least_favorite = "what is your least favorite part of working for a DAO?",
       other = "Is there anything we didnt ask you want to tell us?",
       email = "whats a good email in case we have follow up questions?",
       improve_comp = "are there any opportunities to improve the way you are compensated?  if so what are they?",
       comms_tool = "what comms tools does your DAO use to coordinate?",
       comp_denom = "the majority of your compensation is",
       savings_amount = "how much savings do you have?",
       savings_denom = "most of your savings is in",
       dao_volatility = "how does your DAO handle token volatility?",
       comp_denom_breakdown = "how much of your comp is in DAO Tokens vs stablecoins/ETH?",
       num_field_filled = "Num Fields Filled out",
       include = "Include?",
       valid_res_count = "Valid Response Count"
    ) %>%
    # delete identifying information
    select(-twitter, -eth_addr, -email)


```

## Convert text to tidy text
## What DAO(s) do you work for?

Automatically lowercases, and converts strings to one-token-per-row format to show frequencies and basic bar charts. 

This will be done for each column (question), as a starting point. 

```{r dao, echo=FALSE}
# "what DAO(s) do you work for? for each DAO, how many hours/month do you work? (feel free to include multiple)"
# "daos_work_for" gitcoin/gitcoindao (18 + 5), bankless/banklessdao (13 + 5), 
# dorg (9), metacartel (8), indexcoop (7), daohaus (6), pooltogether (5), moonshot (5), raidguild (4),
# harmony (4), dxdao (4)

daos_work_v <- as.vector(df1$daos_work_for)
daos_work_tbl <- tibble(line = 1:445, text = daos_work_v)

daos_work_tbl %>%
    unnest_tokens(word, text) %>%
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 3) %>%
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "what DAO(s) do you work for?",
        subtitle = "count > 3",
        y = "text",
        x = "count"
    )

```

#### Cleaning data to identify DAOs people work in

To fully answer What DAO(s) do you work for?, we have to isolate all words and 

```{r}

# Unique DAO names

# marrow, mstable, cre8rdao, badger, raidguild, metagame, metafactory, defiant pixel, nfdao, punks, cedgedao, sushi, dalten, metacartel, metacartel ventures, bankless, tally, friends, pleasrdao, seed, forefront, fingerprints, gitcoin, superrare, makerdao, dorg, railgun, mycryptoheroes, daohaus, uber haus, hero dao, indexcoop, dao square, rarible dao, genesis dao, dappnode, radiologex, gridology, yam, alchemy, 1hive, pharo dao, pooltogether, commitpool, machi x dao, peerion dao, doingud, uniswap, gryffone, harmony dao, buidlguidl, airswap.io, aave grants, sourcecred, good ghosting, proof of beauty hash, meebits dao, alas dao, buzzed bear hideout, mcn ventures, fraktal dao, decrypt, synthetix, balancer, flow community, daosquare, aladdindao, sandao, compound, gamedao, halodao, qidao, soudao, curve dao, coordinape, nash dao, discord, ocean, parity, sporkdao, epns, scribedao, trips community, daostack, opolis, aragon, renaissancedao, rabbit hole, cryptex, olympus, mirror

daos_work_long <- daos_work_tbl %>%
    unnest_tokens(word, text) %>%
    anti_join(stop_words) %>% 
    count(word, sort = TRUE)

daos_work_long$bin <- NA

daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "cre8")==TRUE), "cre8rdao", "NA")
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "mstable")==TRUE), "mstable", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "marrow")==TRUE), "marrow dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "badger")==TRUE), "badger dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "raid")==TRUE), "raid guild", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "metagame")==TRUE), "metagame", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "metaf")==TRUE), "metafactory", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "defiant")==TRUE), "defiant pixel society", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "nfd")==TRUE), "nfdao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "punks")==TRUE), "punks dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "cedge")==TRUE), "cedge dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "sushi")==TRUE), "sushi protocol", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "dal")==TRUE), "dalten collective", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "ventures")==TRUE), "metacartel ventures", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "metacartel")==TRUE), "metacartel", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "bank")==TRUE), "bankless dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "tally")==TRUE), "tally", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "friend")==TRUE), "friends with benefits", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "fwb")==TRUE), "friends with benefits", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "pleas")==TRUE), "pleasrdao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "seed")==TRUE), "seed club", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "fore")==TRUE), "forefront", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "finger")==TRUE), "fringerprints", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "gitc")==TRUE), "gitcoin dao / gitcoin", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "gtc")==TRUE), "gitcoin dao / gitcoin", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "super")==TRUE), "superrare dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "daomaker")==TRUE), "daomaker", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "maker")==TRUE), "makerdao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "mkrdao")==TRUE), "makerdao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "makedaos")==TRUE), "makerdao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "dorg")==TRUE), "dOrg", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "rail")==TRUE), "railgun", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "mycryptoh")==TRUE), "mycryptoheroes", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "daoh")==TRUE), "daohaus", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "uber")==TRUE), "uber haus", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "hero_")==TRUE), "hero dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "index")==TRUE), "index coop", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "square")==TRUE), "dao square", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "rally")==TRUE), "rally.io", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "rarible")==TRUE), "rarible dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "genosis")==TRUE), "genesis dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "dappnode")==TRUE), "dappnode", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "radiologex")==TRUE), "radiologex", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "gridology")==TRUE), "gridology", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "yam")==TRUE), "yam", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "alchemy")==TRUE), "alchemy", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "1hive")==TRUE), "1hive", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "pharo")==TRUE), "pharo dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "poolt")==TRUE), "pooltogether", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "commitpool")==TRUE), "commitpool", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "machix")==TRUE), "machi x dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "peerion")==TRUE), "peerion dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "dxdao")==TRUE), "dxdao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "karma")==TRUE), "karma dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "doingud")==TRUE), "doingud", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "unis")==TRUE), "uniswap", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "gryffone")==TRUE), "gryffone", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "harmony")==TRUE), "harmony dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "buidl")==TRUE), "buidlguidl", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "airs")==TRUE), "airswap.io", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "aave")==TRUE), "aave grants", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "sourcecred")==TRUE), "sourcecred", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "ghosting")==TRUE), "goodghosting", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "beauty")==TRUE), "historians dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "historian")==TRUE), "historians dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "meebit")==TRUE), "meebits dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "alas")==TRUE), "alas dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "buzz")==TRUE), "buzzed bear hideout", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "mcn")==TRUE), "mcn ventures", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "fraktal")==TRUE), "fraktal dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "decrypt")==TRUE), "decrypt", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "pollen")==TRUE), "pollen dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "synthetix")==TRUE), "synthetix", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "balancer")==TRUE), "balancer", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "flow")==TRUE), "flow community", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "daosquare")==TRUE), "daosquare", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "daosuqre")==TRUE), "daosquare", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "aladdindao")==TRUE), "aladdindao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "aladdin")==TRUE), "aladdindao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "sandao")==TRUE), "sandao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "compound")==TRUE), "compound", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "gamedao")==TRUE), "gamedao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "halo")==TRUE), "halodao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "qidao")==TRUE), "qidao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "soudao")==TRUE), "soudao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "curve")==TRUE), "curve dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "coordinape")==TRUE), "coordinape", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "nash")==TRUE), "nash dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "discord")==TRUE), "discord", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "ocean")==TRUE), "ocean dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "parity")==TRUE), "parity", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "sporkdao")==TRUE), "sporkdao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "epns")==TRUE), "ethereum push notification service", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "scribedao")==TRUE), "scribeddao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "trips")==TRUE), "trips community", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "daostack")==TRUE), "daostack", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "opolis")==TRUE), "opolis", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "aragon")==TRUE), "aragon", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "renaissancedao")==TRUE), "renaissancedao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "rabbhithole")==TRUE), "rabbithole", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "cryptex")==TRUE), "cryptex.finance", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "olympus")==TRUE), "olympus dao", daos_work_long$bin)
daos_work_long$bin <- if_else((str_detect(daos_work_long$word, "mirror")==TRUE), "mclubdao", daos_work_long$bin)

daos_work_long %>%
    filter(bin != "NA") %>%
    select(bin, n) %>%
    ggplot(aes(x = reorder(bin, n), y = n, fill = bin)) +
    geom_col() +
    theme_minimal() +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)
    ) +
    labs(
        x = "DAOs / Protocols",
        y = "Number of Responses"
    )
    

```

## What DAO(s) do you work in?

Manual data munging needed. 

```{r, echo=FALSE}

# Create new df
daos_work_long2 <- daos_work_long %>%
    filter(bin != "NA") %>%
    select(bin, n) %>%
    arrange(bin)

# manually add same DAOs different rows together
# airswap.io = 2
daos_work_long2$n[3] <- 2

# aladdindao = 4
daos_work_long2$n[5] <- 4

# bankless dao = 35
daos_work_long2$n[12] <- 35

# cedgedao = 2
daos_work_long2$n[18] <- 2

# cre8rdao = 5
daos_work_long2$n[23] <- 5

# daosquare = 10
daos_work_long2$n[30] <- 10

# flow community = 3
daos_work_long2$n[41] <- 3

# friends with benefits = 2
daos_work_long2$n[45] <- 2

# gitcoin = 29
daos_work_long2$n[50] <- 29

# historians dao = 3
daos_work_long2$n[60] <- 3

# index coop = 15
daos_work_long2$n[62] <- 15

# makerdao = 8
daos_work_long2$n[66] <- 8

# metafactory = 3
daos_work_long2$n[77] <- 3

# mstable = 5
daos_work_long2$n[80] <- 5

# olympus dao = 3
daos_work_long2$n[86] <- 3

# pooltogether = 7
daos_work_long2$n[94] <- 7

# raid guild = 8
daos_work_long2$n[99] <- 8

# rally.io = 2
daos_work_long2$n[102] <- 2

# manually delete duplicate rows
# safe in new df
daos_work_long3 <- daos_work_long2[-c(4, 6, 13, 14, 15, 19, 24, 28, 31, 42, 46, 51, 52, 53,
                  61, 63, 67, 68, 69, 70, 78, 81, 87, 95, 100, 103),] %>% 
    arrange(desc(n))

# visualize
daos_work_long3 %>%
    filter(n > 1) %>%
    ggplot(aes(x = n, y = reorder(bin, n), fill = bin)) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    theme_minimal() +
    theme(
        legend.position = "none",
        panel.grid.major = element_line(colour = "white"),
        panel.grid.minor = element_line(colour = "white")
    ) +
    scale_fill_manual(values = c("#9ecae1", "#252525", "#525252",
                                 "#737373", "#969696", "#bdbdbd",
                                 "#d9d9d9", "#f0f0f0", "#ffffff",
                                 "#08306b", "#08519c", "#2171b5", 
                                 "#4292c6", "#6baed6", "#9ecae1", 
                                 "#c6dbef", "#deebf7", "#f7fbff",
                                 "#081d58", "#253494", "#225ea8",
                                 "#525252", "#000000", "#252525", 
                                 "#737373", "#969696", "#bdbdbd",
                                 "#d9d9d9", "#f0f0f0", "#ffffff",
                                 "#08306b", "#08519c", "#2171b5", 
                                 "#4292c6", "#6baed6", "#9ecae1", 
                                 "#c6dbef", "#deebf7", "#f7fbff",
                                 "#081d58", "#253494", "#225ea8",
                                 "#525252", "#525252", "#4292c6", 
                                 "#6baed6", "#000000")) +
    labs(
        title = "What DAO(s) do you work in?",
        subtitle = "Responses (n = 422)",
        x = "Number of Respondents",
        y = ""
    )

```


## What city are you based in?

```{r, echo=FALSE}

city_v <- as.vector(df1$city)
city_tbl <- tibble(line = 1:445, text = city_v)

city_tbl %>%
    unnest_tokens(word, text) %>%
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 2) %>%
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "What city are you based in?",
        subtitle = "count > 2",
        y = "text",
        x = "count"
    )

```

## What kind of work do you do? (eg ops, coder, design, etc)

```{r, echo=FALSE}

task_v <- as.vector(df1$task)
task_tbl <- tibble(line = 1:445, text = task_v)

task_tbl %>%
    unnest_tokens(word, text) %>%
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 3) %>%
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "What kind of work do you do?",
        subtitle = "count > 3",
        y = "text",
        x = "count"
    )
```

## What kind of work do you do? (What role do you play?) (better visual)

Cleaner way to present data. More manual process. Split string by comma, unnest, then mnaully add duplicates, then manually delete, then visualize.

```{r, echo=FALSE}

# What role do you play in your DAO?
# What kind of work do you do? (eg ops, coder, design, etc)

task_v <- as.vector(df1$task)
task_tbl <- tibble(line = 1:445, text = task_v)

# create task_tabl2
task_tabl2 <- task_tbl %>%
    mutate(phrase = strsplit(as.character(text), ",")) %>%
    unnest(phrase) %>%
    count(phrase, sort = TRUE) %>%
    drop_na() %>%
    filter(n > 5)

# manual addition
task_tabl2$n[2] <- 180
task_tabl2$n[3] <- 127
task_tabl2$n[4] <- 118
task_tabl2$n[5] <- 90
task_tabl2$n[6] <- 83
task_tabl2$n[7] <- 86
task_tabl2$n[8] <- 80
task_tabl2$n[10] <- 105
task_tabl2$n[12] <- 55
task_tabl2$n[16] <- 26

# manual deletion (create new table)
task_tabl3 <- task_tabl2[-c(9, 13, 14, 15, 17, 18, 19, 20, 21, 22),] 

# visualize (with task_tabl3)
task_tabl3 %>%
    arrange(desc(n)) %>% 
    ggplot(aes(x = reorder(phrase, n), y = n, fill = phrase)) +
    geom_col() +
    scale_fill_manual(values = c("#000000", "#252525", "#525252",
                                 "#737373", "#969696", "#bdbdbd",
                                 "#d9d9d9", "#f0f0f0", "#ffffff",
                                 "#08306b", "#08519c", "#2171b5", 
                                 "#4292c6", "#6baed6", "#9ecae1", 
                                 "#c6dbef", "#deebf7", "#f7fbff",
                                 "#081d58", "#253494", "#225ea8",
                                 "#525252")) +
    geom_text(aes(label = n), vjust = -0.5) +
    theme_minimal() +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 0.8),
        panel.grid.major = element_line(colour = "white"),
        panel.grid.minor = element_line(colour = "white")
    ) +
    labs(
        title = "What role do you play in your DAO?",
        subtitle = "Responses (n = 422)",
        x = "",
        y = "Number of Responses"
    )
```


## How are tasks assigned?

```{r, echo=FALSE}

task_assign_v <- as.vector(df1$task_assign)
task_assign_tbl <- tibble(line = 1:445, text = task_assign_v)

task_assign_tbl %>%
    unnest_tokens(word, text) %>%
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 4) %>%
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "How are tasks assigned?",
        subtitle = "count > 4",
        y = "text",
        x = "count"
    )

```


## What is your day to day like?

```{r, echo=FALSE}

day_to_day_v <- as.vector(df1$day_to_day)
day_to_day_tbl <- tibble(line = 1:445, text = day_to_day_v)

day_to_day_tbl %>%
    unnest_tokens(word, text) %>%
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 4) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "What is your day to day like?",
        subtitle = "count > 4",
        y = "text",
        x = "count"
    )

```


## Do you have a DAO version of “resume”?

```{r, echo=FALSE}

resume_v <- as.vector(df1$resume)
resume_tbl <- tibble(line = 1:445, text = resume_v)

resume_tbl %>%
    unnest_tokens(word, text) %>%
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 2) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "Do you have a DAO version of “resume”?",
        subtitle = "count > 2",
        y = "text",
        x = "count"
    )

```


## Are there any opportunities to improve the way your work is coordinated?

```{r, echo=FALSE}

improve_coord_v <- as.vector(df1$improve_coord)
improve_coord_tbl <- tibble(line = 1:445, text = improve_coord_v)

improve_coord_tbl %>%
    unnest_tokens(word, text) %>%
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 3) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "Are there any opportunities to improve the way your work is coordinated?",
        subtitle = "count > 3",
        y = "text",
        x = "count"
    )

```


## What web3 tools are used to coordinate/allocate resources?

```{r, echo=FALSE}

# What web tool do you use?

web3_tool_v <- as.vector(df1$web3_tool)
web3_tool_tbl <- tibble(line = 1:445, text = web3_tool_v)

# expand color palette


web3_tool_tbl %>%
    unnest_tokens(word, text) %>%
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>% 
    filter(n > 3) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n), fill = word)) +
    geom_col() +
    scale_fill_manual(values = c("#000000", "#252525", "#525252",
                                  "#737373", "#969696", "#bdbdbd",
                                  "#d9d9d9", "#f0f0f0", "#08306b",
                                  "#08519c", "#2171b5", "#4292c6",
                                  "#6baed6", "#9ecae1", "#c6dbef",
                                  "#deebf7")) +
    geom_text(aes(label = n), hjust = -0.5) +
    theme_minimal() +
    theme(
        legend.position = "none",
        panel.grid.major = element_line(colour = "white"),
        panel.grid.minor = element_line(colour = "white")
    ) +
    labs(
        title = "What web3 tools are used to coordinate/allocate resources?",
        subtitle = "Responses (n = 422)",
        y = "Tools",
        x = "Number of Responses"
    )


```


## How much do you make in USD equivilent per month?

```{r, echo=FALSE}

usd_earning_v <- as.vector(df1$usd_earning)
usd_earning_tbl <- tibble(line = 1:445, text = usd_earning_v)

# save new df to filter if row contains a numeric value
# removing responses where n = 1
usd_earning_tbl2 <- usd_earning_tbl %>%
    count(text, sort = TRUE) %>%
    drop_na() %>%
    filter(n > 1) %>%
    arrange(desc(text)) %>%
    slice(6:15)

# manually add response from 10000 to $7k - $10k
usd_earning_tbl2$n[1] <- 12

# reorder rows, save as new df
usd_earning_tbl3 <- usd_earning_tbl2 %>%
    slice(4, 6, 7, 1:3, 5, 8:9)

# need to sort by factors
    
usd_earning_tbl3 %>% 
    mutate(text_factor = as_factor(text)) %>% 
    ggplot(aes(x = text_factor, y = n, fill = text)) +
    geom_col() +
    geom_text(aes(label = n), vjust = -0.5) +
    scale_fill_manual(values = c("#08306b", "#08519c", "#2171b5",
                                 "#4292c6", "#6baed6", "#9ecae1",
                                 "#525252", "#737373", "#969696")) +
    theme_minimal() +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
        panel.grid.major = element_line(colour = "white"),
        panel.grid.minor = element_line(colour = "white")
    ) +
    labs(
        title = "How much do you make in USD equivalent per month?",
        subtitle = "Responses (n = 422)",
        x = "",
        y = "Number of Responses"
    )

```


## Is your income stability a priority for you? 

```{r, echo=FALSE}

income_stability_v <- as.vector(df1$income_stability)
income_stability_tbl <- tibble(line = 1:445, text = income_stability_v)

income_stability_tbl %>%
    unnest_tokens(word, text) %>%
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 3) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "Is your income stability a priority for you?",
        subtitle = "count > 3",
        y = "text",
        x = "count"
    )

```


## Are DAOs your primary source of income?

NOTE: We want to keep stop words like 'no' or 'yes' here. 

```{r, echo=FALSE}

primary_income_v <- as.vector(df1$primary_income)
primary_income_tbl <- tibble(line = 1:445, text = primary_income_v)

primary_income_tbl %>%
    count(text, sort = TRUE) %>%
    drop_na() %>%
    filter(n > 1) %>%
    ggplot(aes(x = reorder(text, n), y = n, fill = text)) +
    geom_col() +
    scale_fill_manual(values = c("#000000", "#2171b5", "#08519c",
                                 "#4292c6")) +
    geom_text(aes(label = n), vjust = -0.5) +
    theme_minimal() +
    theme(
        legend.position = "none",
        panel.grid.major = element_line(colour = "white"),
        panel.grid.minor = element_line(colour = "white"),
        axis.text.x = element_text(size = 10)
    ) +
    labs(
        title = "Are DAOs your primary source of income?",
        subtitle = "Responses (n = 422)",
        x = "",
        y = "Number of Responses"
    )

```


## How do you handle token volatility?

```{r, echo=FALSE}

token_volatility_v <- as.vector(df1$token_volatility)
token_volatility_tbl <- tibble(line = 1:445, text = token_volatility_v)

token_volatility_tbl %>%
    unnest_tokens(word, text) %>% 
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 6) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "How do you handle token volatility?",
        subtitle = "count > 6",
        y = "text",
        x = "count"
    )

```


## Where do you get health insurance?

```{r, echo=FALSE}

health_insurance_v <- as.vector(df1$health_insurance)
health_insurance_tbl <- tibble(line = 1:445, text = health_insurance_v)

# split string by comma
# unnest, then group,tally
# save as new df
health_insurance_tbl2 <- health_insurance_tbl %>%
    mutate(phrase = strsplit(as.character(text), ",")) %>%
    unnest(phrase) %>%
    count(phrase, sort = TRUE) %>%
    drop_na() %>%
    filter(n > 1)

# manually add items in same category
health_insurance_tbl2$n[2] <- 120
health_insurance_tbl2$n[3] <- 77
health_insurance_tbl2$n[6] <- 44

# select rows through slice, then visualize
health_insurance_tbl2 %>%
    slice(1:3, 6, 8) %>%
    ggplot(aes(x = n, y = reorder(phrase, n), fill = phrase)) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    scale_fill_manual(values = c("#08306b", "#08519c", "#2171b5",
                                 "#525252", "#969696")) +
    theme_minimal() +
    theme(
        legend.position = "none",
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(hjust = 1.1),
        panel.grid.major = element_line(colour = "white"),
        panel.grid.minor = element_line(colour = "white")
    ) +
    labs(
        title = "Where do you get health insurance?",
        subtitle = "Total Survey Responses (n = 422)",
        x = "Number of Respondents",
        y = ""
    )


```


## Are you saving for retirement?

```{r, echo=FALSE}

retirement_v <- as.vector(df1$retirement)
retirement_tbl <- tibble(line = 1:445, text = retirement_v)


# unnesting words to count with "yes" and "no"
# other words counted include: "not" (not yet) (23), "nope" (3)
# alternatives to 'yes': "yse" (1), "yup" (1), "yeah" (4), "sure" (3), "yep" (3)
# slice to only yes or no
retirement_tbl2 <- retirement_tbl %>%
    unnest_tokens(word, text) %>% 
    count(word, sort = TRUE) %>%
    drop_na() %>%
    slice(1:2)

# manually add alternatives to "yes" and "no
retirement_tbl2$n[1] <- 220
retirement_tbl2$n[2] <- 89

# compute position of label, save new df
retirement_tbl3 <- retirement_tbl2 %>%
    arrange(desc(word)) %>%
    mutate(prop = n / sum(retirement_tbl2$n) * 100) %>%
    mutate(ypos = cumsum(prop) - 0.5*prop)


    

# visualize as bar chart
retirement_tbl3 %>%
    mutate(
        prop2 = format(round(prop, 2), nsmall = 2)
    ) %>%
    ggplot(aes(x=word, y=n, fill=word)) +
    geom_col() +
    geom_text(aes(label = n), vjust = -0.5) +
    scale_fill_manual(values = c("#969696", "#08306b")) +
    theme_minimal() +
    theme(
        legend.position = "none",
        axis.text.x = element_text(size = 10),
        panel.grid.major = element_line(colour = "white"),
        panel.grid.minor = element_line(colour = "white")
    ) +
    labs(
        title = "Are you saving for retirement?",
        subtitle = "Total Survey Responses (n = 422)",
        x = "",
        y = "Number of Responses"
    )


```


## How do you do compliance with local taxation/legal requirements for workers?

```{r, echo=FALSE}

tax_v <- as.vector(df1$tax)
tax_tbl <- tibble(line = 1:445, text = tax_v)

tax_tbl %>%
    unnest_tokens(word, text) %>% 
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 6) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "How do you do compliance with taxes?",
        subtitle = "count > 6",
        y = "text",
        x = "count"
    )

```


## What do you do if there is a dispute between yourself and the DAO?

```{r, echo=FALSE}

dispute_v <- as.vector(df1$dispute)
dispute_tbl <- tibble(line = 1:445, text = dispute_v)

dispute_tbl %>%
    unnest_tokens(word, text) %>% 
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 6) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "What do you do if there is a dispute between yourself and the DAO?",
        subtitle = "count > 6",
        y = "text",
        x = "count"
    )
```


## How do you manage visas to travel/work abroad?

```{r, echo=FALSE}


visa_v <- as.vector(df1$visa)
visa_tbl <- tibble(line = 1:445, text = visa_v)

visa_tbl %>%
    unnest_tokens(word, text) %>% 
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 3) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "How do you manage visas to travel/work abroad?",
        subtitle = "count > 3",
        y = "text",
        x = "count"
    )
```


## What is the most different/interesting thing about working for a DAO to you?

```{r, echo=FALSE}


dao_different_v <- as.vector(df1$dao_different)
dao_different_tbl <- tibble(line = 1:445, text = dao_different_v)

dao_different_tbl %>%
    unnest_tokens(word, text) %>% 
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 3) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "What is the most different/interesting thing about working for a DAO to you?",
        subtitle = "count > 3",
        y = "text",
        x = "count"
    )
```



## What is your favorite part of working for a DAO?

```{r, echo=FALSE}


favorite_v <- as.vector(df1$favorite)
favorite_tbl <- tibble(line = 1:445, text = favorite_v)

favorite_tbl %>%
    unnest_tokens(word, text) %>% 
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 3) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "What is your favorite part of working for a DAO?",
        subtitle = "count > 3",
        y = "text",
        x = "count"
    )
```


## What is your least favorite part of working for a DAO?

```{r, echo=FALSE}

least_favorite_v <- as.vector(df1$least_favorite)
least_favorite_tbl <- tibble(line = 1:445, text = least_favorite_v)

least_favorite_tbl %>%
    unnest_tokens(word, text) %>% 
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 3) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "What is your least favorite part of working for a DAO?",
        subtitle = "count > 3",
        y = "text",
        x = "count"
    )

```


## Is there anything we didnt ask you want to tell us?

```{r, echo=FALSE}

other_v <- as.vector(df1$other)
other_tbl <- tibble(line = 1:445, text = other_v)

other_tbl %>%
    unnest_tokens(word, text) %>% 
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 3) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "Is there anything we didnt ask you want to tell us?",
        subtitle = "count > 3",
        y = "text",
        x = "count"
    )

```


## Are there any opportunities to improve the way you are compensated?

```{r, echo=FALSE}

improve_comp_v <- as.vector(df1$improve_comp)
improve_comp_tbl <- tibble(line = 1:445, text = improve_comp_v)

improve_comp_tbl %>%
    unnest_tokens(word, text) %>% 
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 3) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "Are there any opportunities to improve the way you are compensated?",
        subtitle = "count > 3",
        y = "text",
        x = "count"
    )


```


## What comms tools does your DAO use to coordinate?

```{r, echo=FALSE}


comms_tool_v <- as.vector(df1$comms_tool)
comms_tool_tbl <- tibble(line = 1:445, text = comms_tool_v)

comms_tool_tbl %>%
    unnest_tokens(word, text) %>% 
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 3) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col(aes(fill = word)) +
    scale_fill_manual(values = c("#000000", "#252525", "#525252",
                                 "#737373", "#969696", "#bdbdbd",
                                 "#d9d9d9", "#f0f0f0", "#08306b",
                                 "#08519c", "#2171b5", "#4292c6",
                                 "#6baed6", "#9ecae1", "#c6dbef",
                                 "#deebf7")) +
    geom_text(aes(label = n), hjust = -0.5) +
    theme_minimal() +
    theme(
        legend.position = "none",
        panel.grid.major = element_line(colour = "white"),
        panel.grid.minor = element_line(colour = "white")
    ) +
    labs(
        title = "What communications tools does your DAO use to coordinate?",
        subtitle = "Responses (n = 422)",
        y = "Tools",
        x = "Number of Responses"
    )


```


## The majority of your compensation is from (i.e., Source of Compensation)


```{r, echo=FALSE}

# The majority of your compensation is from ----

comp_denom_v <- as.vector(df1$comp_denom)
comp_denom_tbl <- tibble(line = 1:445, text = comp_denom_v)

# split string by comma
# unnest from vector
# group_by and sort (count)
# save as new df

comp_denom_tbl2 <- comp_denom_tbl %>%
    mutate(phrase = strsplit(as.character(text), ",")) %>%
    unnest(phrase) %>%
    count(phrase, sort = TRUE) %>%
    drop_na()

# manually add same compensation categories
comp_denom_tbl2$n[1] <- 158
comp_denom_tbl2$n[3] <- 159
comp_denom_tbl2$n[8] <- 104
comp_denom_tbl2$n[6] <- 78
comp_denom_tbl2$n[11] <- 55

# select specific rows, then visualize
comp_denom_tbl2 %>%
    slice(1,3,4,6,8,11) %>%
    arrange(desc(n)) %>%
    ggplot(aes(x = reorder(phrase,n), y = n, fill = phrase)) +
    geom_col() +
    geom_text(aes(label = n), vjust = -0.5) +
    scale_fill_manual(values = c("#08306b", "#08519c", "#2171b5",
                                 "#525252", "#737373", "#969696")) +
    theme_minimal() +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
        panel.grid.major = element_line(colour = "white"),
        panel.grid.minor = element_line(colour = "white")
    ) +
    labs(
        title = "Source of Compensation",
        subtitle = "Total Survey Responses (n = 422)",
        x = "",
        y = "Number of Responses"
    )


```


## How much savings do you have?

```{r, echo=FALSE}

savings_amount_v <- as.vector(df1$savings_amount)
savings_amount_tbl <- tibble(line = 1:445, text = savings_amount_v)

savings_amount_tbl %>%
    count(text, sort = TRUE) %>%
    drop_na() %>%
    ggplot(aes(n, reorder(text, n))) +
    geom_col(aes(fill = text)) +
    scale_fill_manual(values = c("#525252", "#969696", "#4292c6", "#6baed6")) +
    geom_text(aes(label = n), hjust = -0.5) +
    theme_minimal() +
    theme(
        legend.position = "none",
        panel.grid.major = element_line(colour = "white"),
        panel.grid.minor = element_line(colour = "white")
    ) +
    labs(
        title = "How much savings do you have?",
        subtitle = "Responses (n = 422)",
        y = "Runway",
        x = "Number of Responses"
    )

```


## Most of your savings is in

```{r, echo=FALSE}

savings_denom_v <- as.vector(df1$savings_denom)
savings_denom_tbl <- tibble(line = 1:445, text = savings_denom_v)

savings_denom_tbl %>%
    #unnest_tokens(word, text) %>% 
    #anti_join(stop_words) %>%
    count(text, sort = TRUE) %>% 
    filter(n > 3) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(text, n))) +
    geom_col(aes(fill = text)) +
    coord_flip() +
    scale_fill_manual(values = c("#4292c6", "#525252", "#969696")) +
    geom_text(aes(label = n), vjust = -1) +
    theme_minimal() +
    theme(
        legend.position = "none",
        panel.grid.major = element_line(colour = "white"),
        panel.grid.minor = element_line(colour = "white")
    ) +
    labs(
        title = "Most of your savings is in which asset?",
        subtitle = "Responses (n = 422)",
        y = "Asset",
        x = "Number of Responses"
    )



```


## How does your DAO handle token volatility?

```{r, echo=FALSE}


dao_volatility_v <- as.vector(df1$dao_volatility)
dao_volatility_tbl <- tibble(line = 1:445, text = dao_volatility_v)

dao_volatility_tbl %>%
    unnest_tokens(word, text) %>% 
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 3) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "How does your DAO handle token volatility?",
        subtitle = "count > 3",
        y = "text",
        x = "count"
    )
```


## How much of your comp is in DAO Tokens vs stablecoins/ETH?

Response options for this question are too unclear to make sense. Will prioritize other charts then come back to this one with sufficient time.

```{r, echo=FALSE}

comp_denom_breakdown_v <- as.vector(df1$comp_denom_breakdown)
comp_denom_breakdown_tbl <- tibble(line = 1:445, text = comp_denom_breakdown_v)

comp_denom_breakdown_tbl %>%
    unnest_tokens(word, text) %>% 
    anti_join(stop_words) %>%
    count(word, sort = TRUE) %>%
    filter(n > 3) %>% 
    drop_na() %>%
    ggplot(aes(n, reorder(word, n))) +
    geom_col() +
    geom_text(aes(label = n), hjust = -0.5) +
    labs(
        title = "How much of your comp is in DAO Tokens vs stablecoins/ETH?",
        subtitle = "count > 3",
        y = "text",
        x = "count"
    )
```


## Num Fields Filled out

## Include

## Valid Response Count

## Testing

```{r, echo=FALSE}

```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
